Online (Bandit) Policy Selection for EASY-Backfilling

### 2017-04-02 paper/src/paper.tex
changes for release.

\acmConference[SC’15]{Supercomputing}{May 29 -- June 2}{Orlando, FL, USA}

@@

Our main results are as follows: The approach based on the simulator provides
very good results, close to the best policy in the search set. In essence, this
means that we are able to recover in an online fashion existing results that
divide average waiting times by factor of \textcolor{orange}{X} to
\textcolor{orange}{X}. Indeed, we show that the required sample sizes for
policy selection in batch schedulers are small enough for workload resampling to
be avoided in practice. The variant based on noisy data, which is closer to
actual conditions of uncertainties on both jobs and platform, also behaves very
well. The alternate approach based on a multi-armed bandit also provides
reasonable results at a much lower cost, dividing the average waiting times by
a factor of \textcolor{orange}{X} to \textcolor{orange}{X}.

@@

\begin{table*}[]
  \centering
  \ra{1.3}
  \caption{Average Cumulative waiting time improvement with respect to EASY-FCFS of fixed policies.}
  \label{tab:strat}
  \begin{tabular}{@{}lrrrrrrrrrrr@{}}
    \hline
    Trace        & Random &      & Full &      & Noisy &      & Bandit & \\
    \hline
    $\Delta$     & day    & week & day  & week & day   & week & day    & week\\
    CTC-SP2      & -20    &      & -44  &      & -44   &      & -26    & \\
    KTH-SP2      & -6     &      & -12  &      & -12   &      & -7     & \\
    SDSC-SP2     & -4     &      & -13  &      & -13   &      & -5     & \\
    SDSC-BLUE    & -12    &      & -31  &      & -30   &      & -12    & \\
    ANL-Intrepid & -13    &      & -22  &      & -19   &      & -13    & \\
    CEA-Curie    & -35    &      & -53  &      & -53   &      & -36    & \\
    Unilu-Gaia   & -29    &      & -59  &      & -58   &      & -33    & \\
    \hline
  \end{tabular}
\end{table*}

@@

\textbf{Full vs Bandit feedback.} As expected, the bandit strategy evolves
between the random strategy and the full feedback strategy.
It is able to recover between \textcolor{orange}{X\%} to \textcolor{orange}{X\%}
of the Random-FullFeedback gap.

@@

This approach was used in two methods: a method based on a simulator and a
method based on a multi-armed bandit algorithm. The first one provides very good results,
improving the average waiting times of the baseline FCFS ordering policy by a
factor of \textcolor{orange}{X} to \textcolor{orange}{X} The second one is
slighly less efficient with an improvement factor of  \textcolor{orange}{X} to
\textcolor{orange}{X}. However, it is more easy to use and less costly to run.

@@

   \item[simulation]: This step runs the lightweight ocaml backfilling
     simulator specially written for this work. this simulator is made
     available under the isc~\cite{isc} license both as a persistent zenodo
     archive at~\cite{ocst} and as a git repository at ~\cite{ocstgit}.

>>>>

\acmConference[SC’17]{Supercomputing}{May 29 -- June 2}{Orlando, FL, USA}

@@

Our main results are as follows: The approach based on the simulator provides
very good results, close to the best policy in the search set. In essence, this
means that we are able to recover in an online fashion existing results that
reduce average waiting times between -11\% and -60\% compared to EASY-FCFS.
Indeed, we show that the required sample sizes for policy selection in batch
schedulers are small enough for workload resampling to be avoided in practice.
The variant based on noisy data, which is closer to actual conditions of
uncertainties on both jobs and platform, also behaves very well. The alternate
approach based on a multi-armed bandit also provides reasonable results at a
much lower cost, reducing the average waiting times down to between -8\% and
-46\% compared to EASY-FCFS.

@@

\begin{table*}[]
  \centering
  \ra{1.3}
  \caption{Average Cumulative waiting time improvement of the proposed policies with respect to EASY(FCFS).}
  \label{tab:strat}
  \begin{tabular}{@{}lrrrrrrrrrrr@{}}
    \hline
    Trace        & Random &       & Full  &       & Noisy &       & Bandit & \\
    \hline
    $\Delta$     & week   & day   & week  & day   & week  & day   & week   & day \\
    CTC-SP2      & -20\%  & -23\% & -44\% & -44\% & -44\% & -44\% & -26\%  & -31\% \\
    KTH-SP2      & -6\%   & -8\%  & -12\% & -11\% & -12\% & -12\% & -7\%   & -10\% \\
    SDSC-SP2     & -4\%   & -7\%  & -13\% & -13\% & -13\% & -13\% & -5\%   & -8\% \\
    SDSC-BLUE    & -12\%  & -14\% & -31\% & -31\% & -30\% & -29\% & -12\%  & -17\% \\
    ANL-Intrepid & -13\%  & -20\% & -22\% & -26\% & -19\% & -24\% & -13\%  & -20\% \\
    CEA-Curie    & -35\%  & -42\% & -53\% & -47\% & -53\% & -48\% & -36\%  & -46\% \\
    Unilu-Gaia   & -29\%  & -31\% & -59\% & -60\% & -58\% & -58\% & -33\%  & -34\% \\
    \hline
  \end{tabular}
\end{table*}

@@

\textbf{Full vs Bandit feedback.} As expected, the bandit strategy evolves
between the random strategy and the full feedback strategy. The bandit-based
strategy always fares better with a shorter period $\Delta$, recovering between
a quarter to the whole gap between the Random and Full Feedback strategies.

@@

This approach was used in two methods: a method based on a simulator and a
method based on a multi-armed bandit algorithm. The first one provides very good results,
reducing the average waiting times of the baseline FCFS ordering policy by a
factor of -11\% to -60\%. The second one is
slighly less efficient with an improvement factor of -8\% to
-46\%. However, it is easier to use and less costly to run.

@@

   \item[simulation]: This step runs the lightweight ocaml backfilling
     simulator specially written for this work. this simulator is made
     available under the isc~\cite{isc} license as a persistent zenodo
     archive at~\cite{ocst}.
